\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
Add a missing article in the mapreduce/histogram application section and try using \begin{Code} instead of \begin{verbatim} in that section (seems to be typeset the same, I may try more changes to improve the typsetting of this example).
Steve Scott noticed that one sentence in the conclusion had the word
'other' in it 3 times -- remove one superfluous word as he suggested.

Split another run-on sentence in the conclusion into two sentences as
suggested by Steve as well.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@821 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{verbatim}
  protoc histogram.proto --python_out=.
\end{verbatim}
This generates Python module called \texttt{histogram\_pb2.py}, containing both the 
descriptor information as well as methods to read and manipulate the histogram 
message data.

\begin{verbatim}
# Import modules
from histogram_pb2 import HistogramState;

@@

# Output the histogram
outfile = open("/tmp/hist.pb", "wb")
outfile.write(hist.SerializeToString())
outfile.close()
\end{verbatim}

@@

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.

As the \pkg{RProtoBuf} package provides users with the ability to generate,
parse and manipulate Protocol Buffer messages in R, it is our hope that this
package will make Protocol Buffers more accessible to the R community, and
thereby makes a small contribution towards better integration between R and
other software systems and applications.

>>>>

\begin{verbatim}
  protoc histogram.proto --python_out=.
\end{verbatim}
This generates a Python module called \texttt{histogram\_pb2.py}, containing both the 
descriptor information as well as methods to read and manipulate the histogram 
message data.

\begin{Code}
# Import modules
from histogram_pb2 import HistogramState;

@@

# Output the histogram
outfile = open("/tmp/hist.pb", "wb")
outfile.write(hist.SerializeToString())
outfile.close()
\end{Code}

@@

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with distributed systems written in C++, Java, Python, and 
other languages.

The \pkg{RProtoBuf} package provides users with the ability to generate,
parse and manipulate Protocol Buffer messages in R.  It is our hope that this
package will make Protocol Buffers more accessible to the R community, and
thereby makes a small contribution towards better integration between R and
other software systems and applications.
